Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/example.tex
Answer Konrad's questions is section 4 and 5
Remove hyphen on code contract

The expected behavior of the SW system, and the components
implementing the system, is modeled with AGREE contract
specifications.  The contracts constrain input with assumptions and
state properties of output with guarantees.  AGREE performs model
checking on this assume-guarantee system to hierarchically prove that
the SW component obeys all contract obligations under all possible
finite input streams.  The AGREE analysis, contract language, and
contracts for SW are discussed in greater detail in
\secref{sec:agree}.

@@

The system designer now uses BriefCASE to cyber-harden SW by inserting
high-assurance components in the form of a filter and a monitor, as
shown in \figref{fig:hardened}, to isolate the AI component and prevent it from violating the WM component input assumptions.
A filter enforces an invariant over
each datum in the data stream by not forwarding input to its output if
that input violates the filter invariant.  The auto-generated AGREE
code-contract specification states that only well-formed inputs are passed to the
output.  The system developer must further define the filtering
policy, but it is usually based on the existing assumptions made by
downstream components that consume the filter output.

A monitor captures a relation on input data over time and is thus able
to reason about the temporal, and other invariant, properties of that input.  A monitor raises
an alert if the specified properties are ever violated.  The
AGREE code-contract specification for the monitor in our example states that an
automation response can only be generated in conjunction with an
automation request; and further, that response must come with the
request or in the next step after the request.  As with the filter,
the system designer provides the policy, and that policy is typically
based on existing the assumptions and guarantees of the SW system and its implementing components.
AGREE code-contract specifications are discussed in detail in \secref{sec:code-contracts}.

@@

\subsection{Code synthesis}
High-assurance components are automatically synthesized by SPLAT from
the AGREE code-contract specifications to equivalent programs in the CakeML
language.
%% Too strong at the moment!
%The synthesis toolchain generates a proof that equates the
%% meaning of the AGREE specification to the behavior of the CakeML
%% program.
 In other words, for any set of input streams that meet the
 component's contract assumptions, the output streams produced from
 the synthesized CakeML code exactly match those defined by the
 high-assurance component's guarantees.  The CakeML compiler provides
 verified compilation to binaries for several different platforms,
 meaning that the resulting binaries exactly preserve the meaning of
 the original CakeML code \cite{cakeml}.

>>>>

The expected behavior of the SW system, and the components
implementing the system, is modeled with AGREE contract
specifications.  The contracts constrain input with assumptions and
state properties of output with guarantees.  AGREE performs model
checking on this assume-guarantee system to hierarchically prove that
the SW component obeys all contract obligations under all possible
finite input streams.  The AGREE analysis, contract language, and
contracts for SW are discussed in greater detail in
\secref{sec:agree} and \secref{sec:agree-semantics}.

@@

The system designer now uses BriefCASE to cyber-harden SW by inserting
high-assurance components in the form of a filter and a monitor, as
shown in \figref{fig:hardened}, to isolate the AI component and prevent it from violating the WM component input assumptions.
A filter enforces an invariant over
each datum in the data stream by not forwarding input to its output if
that input violates the filter invariant.  The auto-generated AGREE
code contract specification states that only well-formed inputs are passed to the
output.  The system developer must further define the filtering
policy, but it is usually based on the existing assumptions made by
downstream components that consume the filter output.

A monitor captures a relation on input data over time and is thus able
to reason about the temporal, and other invariant, properties of that input.  A monitor raises
an alert if the specified properties are ever violated.  The
AGREE code contract for the monitor in our example states that an
automation response can only be generated in conjunction with an
automation request; and further, that response must come with the
request or in the next step after the request.  As with the filter,
the system designer provides the policy, and that policy is typically
based on existing the assumptions and guarantees of the SW system and its implementing components.
AGREE code contracts are discussed in detail in \secref{sec:code-contracts}.

@@

\subsection{Code synthesis}
High-assurance components are automatically synthesized by SPLAT from
the AGREE code contracts to equivalent programs in the CakeML
language.
%% Too strong at the moment!
%The synthesis toolchain generates a proof that equates the
%% meaning of the AGREE specification to the behavior of the CakeML
%% program.
 In other words, for any set of input streams that meet the
 component's contract assumptions, the output streams produced from
 the synthesized CakeML code exactly match those defined by the
 high-assurance component's guarantees.  The CakeML compiler provides
 verified compilation to binaries for several different platforms,
 meaning that the resulting binaries exactly preserve the meaning of
 the original CakeML code \cite{cakeml}.
